### 2016-08-03 forgerard.tex
two-population dust model

The best-fit distribution for the parameters $\gamma$  and our measurement of
$\frac{\gamma_X}{\gamma_1-\gamma_2}$  compared with the predictions of CCM dust are shown in Figure~\ref{gamma:fig}:
our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ has significantly smaller
uncertainties and are consistent with $R_V=3.1$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.4in]{output7/gamma_corner.pdf} 
   \includegraphics[width=3.3in]{output7/ccm.pdf} 
   \caption{Left: Best-fit distribution for the parameters $\gamma$.  Right: 68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
   predictions for different values of $R_V$.}
   \label{gamma:fig}
\end{figure}

@@

Add Si line velocity.

\subsection{Two-Color Model}
Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.

\subsubsection{Setup}
\begin{equation*}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
\end{matrix}
\right)
,C_{c}
\right).
\end{equation*}
%\begin{equation*}
%D \sim \mathcal{N}(\bar{D},1)
%\end{equation*}
\begin{equation*}
\left(
\begin{matrix}
U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\end{equation*}
\begin{equation*}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
\end{equation*}

>>>>

The best-fit distribution for the parameters $\gamma$ are shown in Figure~\ref{gamma:fig}.  Our measurement of
$\frac{\gamma_X}{\gamma_1-\gamma_2}$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
uncertainties and are consistent with $R_V=3.1$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3in]{output7/gamma_corner.pdf} 
   \caption{Best-fit distribution for the parameters $\gamma$.  68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
   predictions for different values of $R_V$.}
   \label{gamma:fig}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output7/ccm.pdf}
      \includegraphics[width=2.8in]{output7/ccm2.pdf} 
   \caption{68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
   predictions for these parameters are overlaid for different values of $R_V$.}
   \label{ccm:fig}
\end{figure}

@@

Add Si line velocity.
%
%\subsection{Two-Color Model}
%Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
%Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
%with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
%that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
%
%\subsubsection{Setup}
%\begin{equation*}
%\left(
%\begin{matrix}
%U\\B\\V\\R\\I
%\end{matrix}
%\right) \sim \mathcal{N}
%\left(
%\Delta +
%\left(
%\begin{matrix}
%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
%\end{matrix}
%\right)
%,C_{c}
%\right).
%\end{equation*}
%%\begin{equation*}
%%D \sim \mathcal{N}(\bar{D},1)
%%\end{equation*}
%\begin{equation*}
%\left(
%\begin{matrix}
%U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
%\end{matrix}
%\right) \sim \mathcal{N}
%\left(
%\left(
%\begin{matrix}
%U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
%EW_{Si}\\ EW_{Ca}
%\end{matrix}
%\right)
%,C
%\right).
%\end{equation*}
%\begin{equation*}
%\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
%\end{equation*}
